The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-11 analysis/paper/paper.qmd
Update layout

```{r get-pdf-text}
#| echo: false
#| cache: true
#| message: false

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text_and_location.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu$text_raw <- convert_pdf_text(pdf_paths)

  # Add latitude and longitude information to theses data frame
  emu <- geocode_thesis_locations(emu)

  # Write thesis dataframe to file
  write_csv(emu, data_path)
} else {
  emu$text_raw <- read_csv(data_path)$text
  emu$longitude <- read_csv(data_path)$longitude
  emu$latitude <- read_csv(data_path)$latitude
}

>>>>

```{r load-data}
#| echo: false
#| message: false

# Read thesis metadata
data(emu_metadata)

# Load raw text data
data(emu_raw)

# Join text with the metadata file  
emu <- left_join(emu_raw, emu_metadata, by = "ID")
